Fitness Adventure: an interactive floor game to maintain body fitness

### 2015-01-27 paper.tex
rewrite parts of conclusion and fix some typos and mistakes in the intro

  \begin{abstract}
    We introduce a jump 'n' run game for interactive floors to maintain body fitness. Players control themselves directly by stepping, jumping or laying on the floor. In a forrest, users jump over fallen trees or cross an ocean by holding themselves on ice floes. Repairing a bridge in shortage of time or similar complex tasks pack fitness exercises in an exciting adventure. This motivates users to do regular physical activity.
  \end{abstract}

  \section{Introduction}
    Most of today's tasks are done by machines. The majority of people spend almost the whole day in an office -- sitting.
    Fitness apps for smartphones are getting more and pupular and many people subscripe to local fitness centres. 
    At least the persons we asked about their sports activity in our contextual inquery.

@@

    Justus Wirth (Figure \ref{fig:users_casual} on the left) started doing freelethics in order to maintain health and get a better body. He wants to improve his performance in every training session and somehow get feedback on how well he performed his exercises.

    Carl and Ruben (Figure \ref{fig:users_pro}) from the \emph{Fit in Friedrichshain} fitness centre do bodybuilding on a professional level. Their motivations are also their bodies as well as their jobs. In general the motivation really depends on the individual person. Their clients, however, already bring the necessary motivation. Both, Carl and Ruben, were very interested in the idea of a touch floor exercising application, but mentioned problems regarding gym equipment. ``\emph{Every kind of activity is good.}'' says Carl, ``\emph{but there are no effective exercises for training the shoulders for example}''.

    As a result, we focus on regular activity, instead of building up muscles and offer another approach to motivate activity: a video game. Users embody the protagonist themselves, explore the world and beat their own highscores by completing the level faster. This enables users to improve on every ``\emph{training}'' and also requires more energy and endurance. In addition, the game offers another environment for exercises than the traditional fitness studio and thus addresses other kinds of people.

  \begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{roto_main}
    \caption{doing sport exercises on an interactive floor as part of the game}
    \label{fig:figure1}
  \end{figure}

@@

  When designing applications for interactive floors, user studies and exploration with prototypes becomes extremely imporant since there are no general patterns and the problem domain is yet unexplored. During the process our evaluation of the user's needs changed radically. When asking users what they wanted they looked at existing solutions and tried to map them to the floor. If we followed those, we would have ended up with a fitness mat and a video player. But this is already the solution for people, who want to do fitness without any sport equipment. We collected important aspects from users like the need for motivation and limited free time and mapped them to possible exersices on the floor. Finally we came to the conclusion, that games are the most interactive solution that motivate users with fun when they work out. The ability to challenge your high score pushes your goals and shows you your progress. 
    Since developing an interactive protoype for a floor requires a major amount of work, paper prototyping turned out to be a powerful tool to find design flaws in your prototypes as users were able to imagine the system.
    In addition, even when users want to use an application to do fitness activity, they look for the simplest solution to solve a game. Therefore you need to design fitness games that force users to do certain activity with the desired path instead of giving them the freedom how they want to solve a certain task.

>>>>

  \begin{abstract}
    We introduce a jump 'n' run game for interactive floors to maintain body fitness. Players control themselves directly by stepping, jumping or lying on the floor. In a forest, users jump over fallen trees or cross an ocean by holding themselves on ice floes. Repairing a bridge in shortage of time or similar complex tasks pack fitness exercises in an exciting adventure. This motivates users to do regular physical activity.
  \end{abstract}

  \section{Introduction}
    Most of today's tasks are done by machines. The majority of people spend almost the whole day in an office -- sitting.
    Fitness apps for smartphones are getting more and popular and many people subscribe to local fitness centers. 
    At least, the persons we asked about their sports activity in our contextual inquiry.

@@

    Justus Wirth (Figure \ref{fig:users_casual} on the left) started doing freeletics in order to maintain health and get his body in shape. He wants to improve his performance in every training session and somehow get feedback on how well he performed his exercises.

    Carl and Ruben (Figure \ref{fig:users_pro}) from the \emph{Fit in Friedrichshain} fitness centre do bodybuilding on a professional level. Their motivations consists also of their bodies as well as of their jobs. In general, the motivation depends on the individual person. Their clients, however, already bring the necessary motivation for training. Both, Carl and Ruben, were very interested in the idea of a ``touch floor exercising application'', but mentioned problems regarding gym equipment. ``\emph{Every kind of activity is good}'' says Carl, ``\emph{but there are no effective exercises for training the shoulders for example}''.

  \begin{figure}[!t]
    \centering
    \includegraphics[width=\columnwidth]{roto_main_2}
    \caption{doing sport exercises as part of the game on an interactive floor}
    \label{fig:figure1}
  \end{figure}

    As a result, we focus on regular activity, instead of building up muscles and offer another approach to motivate activity: a video game. Users embody the protagonist themselves, explore the world and beat their own highscores by completing the level faster. This enables users to improve on every ``\emph{training session}'' and also requires more energy and endurance. In addition, the game offers another environment for exercises than the traditional fitness studio and thus addresses other kinds of people.

@@

  When designing applications for interactive floors, user studies and exploration with prototypes becomes extremely important since there are no patterns and the problem domain is yet unexplored. During the process, our evaluation of the users' needs changed radically. When asking users what they wanted they looked at existing solutions and tried to map them to the floor. If we followed those, we would have ended up with a fitness mat and a video player. This, however, is already an existing solution for people without any sport equipment. We collected important aspects from users: the need for motivation and limited free time. First we mapped them to possible exercises on the floor and later came to the conclusion, that games are the most interactive solution motivating users with fun when doing workouts. The ability to challenge your highscore, pushes your goals and visualize your progress. 
  Developing an interactive protoype for a floor requires a lot amount of work. Paper prototyping turned out to be a powerful tool in order to find flaws in our designs as users were able to imagine the system.
  Even when users want to do fitness activity with our application, they look for the simplest solution to solve a game. Therefore we need to design fitness games that forces users to do certain activity instead of giving them the freedom on how they want to solve a task.
